The Eternal Adversary between Censor and Circumvention

### 2025-02-13 paper/paper.tex
minimum plot and text fix for rigor (thanks for the professor, who point out my mistake in data plotting)

\subsubsection{Packet length}
The length of packets that carry the payload, header, and instructions of the proxy protocol is also a significant feature of protocols. An example is Trojan-gfw, which utilizes the TLS protocol stack but does not resize its packets. This leads to some packets with outstanding extreme lengths. 
The following figures that we depict show the occurrences of length respectively for each protocol. 
There are also length statistics of standard HTTPS traffic, which can be the control group. Naiveproxy uses padding and packet resizing to mitigate recognizing and categorization in the aspect of packet length.

@@

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.4\textwidth, height=5cm]{pics/occurrence_of_length_naiveproxy.png}
%     \caption{The length-occurrence statistics of Naiveproxy}
% \end{figure}
\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.40\textwidth}
        \includegraphics[width=\textwidth, height=4cm]{pics/occurrence_of_length_trojan.png}
        \caption{Trojan}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.40\textwidth}
        \includegraphics[width=\textwidth, height=4cm]{pics/occurrence_of_length_https.png}
        \caption{HTTPS}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.40\textwidth}
        \includegraphics[width=\textwidth, height=4cm]{pics/occurrence_of_length_naiveproxy.png}
        \caption{Naiveproxy}
    \end{subfigure}
    \caption{Length-occurrence statistics}
\end{figure}

>>>>

\subsubsection{Packet length}
The length of packets that carry the payload, header, and instructions of the proxy protocol is also a significant feature of protocols. An example is Trojan-gfw, which utilizes the TLS protocol stack but does not resize its packets. This leads to characteristics, which has a recognizable pattern in the temporal domain (a burst of long packets).
The following figures that we depict show the occurrences of length respectively for each protocol. 
There are also length statistics of standard HTTPS traffic, which can be the control group. Naiveproxy uses padding and packet resizing to mitigate recognizing and categorization in the aspect of packet length.

@@

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.4\textwidth, height=5cm]{pics/occurrence_of_length_naiveproxy.png}
%     \caption{The length-occurrence statistics of Naiveproxy}
% \end{figure}
\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.40\textwidth}
        \includegraphics[width=\textwidth, height=4cm]{pics/temporal_statistic_of_length_trojan.png}
        \caption{Trojan}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.40\textwidth}
        \includegraphics[width=\textwidth, height=4cm]{pics/temporal_statistic_of_length_https.png}
        \caption{HTTPS}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.40\textwidth}
        \includegraphics[width=\textwidth, height=4cm]{pics/temporal_statistic_of_length_naiveproxy.png}
        \caption{Naiveproxy}
    \end{subfigure}
    \caption{Length-occurrence statistics}
\end{figure}
